noTCP: extend, extend, repurpose

### 2014-06-13 paper/paper.tex
branch switching commit..

%%%%%%%  Author Notes %%%%%%%
%
\ifnum\shownotes=1
\newcommand{\authnote}[2]{{ $\ll$\textsf{\footnotesize #1 notes: #2}$\gg$}}
\else
\newcommand{\authnote}[2]{}
\fi
\newcommand{\Ynote}[1]{{\authnote{Yan}{#1}}}
\newcommand{\Anote}[1]{{\authnote{Andrius}{#1}}}
\newcommand{\Nnote}[1]{{\authnote{Narseo}{#1}}}
\newcommand{\Vnote}[1]{{\authnote{Vijay}{#1}}}
\newcommand{\Dnote}[1]{{\authnote{Dina}{#1}}}

@@

\begin{table*}[t]
{\small
\begin{center}
\begin{tabular}{| l | >{\centering\arraybackslash}m{0.8cm} | >{\centering\arraybackslash}m{0.9cm} | >{\centering\arraybackslash}m{1.6cm} | >{\centering\arraybackslash}m{1.6cm} | >{\centering\arraybackslash}m{1.6cm} | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{1.cm} | }
\hline
    \textbf{Net ID} & \textbf{No filter} & \textbf{Global IP}   & \textbf{Port-specific} & \textbf{Validate checksum} & \textbf{Drop S/A data} & \textbf{Normalize ACK}  & \textbf{Normalize URG} & \textbf{Normalize Reserved} & \textbf{Remap Seq.} \\ \hline \hline
    % Univ Helsinki WiFi
    WiFi education 1 &                   &                      &                        & \checkmark                 &                        &                         &                        &                             &                     \\ \hline
    % Eduroam
    WiFi education 2 &                   & \checkmark           &                        &                            & \checkmark             &                         & \checkmark \checkmark  &                             & \checkmark          \\ \hline
    % wgb
    WiFi public 1      & \checkmark      &                      &                        &                            &                        &                         &                        &                             &                     \\ \hline
    % Finland internet.saunalahti
    Cellular Finland 1 & \checkmark      &                      &                        &                            &                        &                         &                        &                             &                     \\ \hline
    % Virgin home
    WiFi residential 1 &                 &                      &                        & \checkmark                 &                        &                         &                        &                             &                     \\ \hline
    % GiffGaff
    Cellular UK 1      &                 &                      &  \checkmark (443, 993) & -                          & -                      & -                       & -                      & -                           & -                   \\ \hline            
\end{tabular}
\end{center}
}
\caption{Network behaviour observed through tests generating custom TCP packets. A single checkmark means that particular behaviour was observed or in case of normalization the field was reset or replaced with a valid value. Double checkmark means that specific type of packet was discarded. A dash means that we observed different cases on the same network.}
\label{tab:networks}
\end{table*}

We show our collected results in Table~\ref{tab:networks}. Since we were focusing on mobile applications, we collected data across a number of public, residential and university WiFi networks and cellular networks in XX different countries. The results outline for which networks we did not see any filtering, which ones discarded packets with invalid checksums, normalised particular fields (either dropped packets or reset to different values) and what type of mapping did NATs perform - only port number remapping or also changed sequence numbers.

@@

\begin{quotation}
    Although these examples do not show connection synchronization using data-carrying segments, this is perfectly legitimate...
\end{quotation}

We also tested middlebox itneraction with reserved header bits. We separated our tests to handshake and data exchange parts as well as set each bit individually, however we did not observe different behavior for these: the bits were either passwd through or cleared at both phases, but we did not observe cases when such packets are dropped.

>>>>

%%%%%%%  Author Notes %%%%%%%
%
\ifnum\shownotes=1
\newcommand{\authnote}[2]{{ $\ll$\textsf{\footnotesize #1 notes: #2}$\gg$}}
\else
\newcommand{\authnote}[2]{}
\fi
\newcommand{\Anote}[1]{{\authnote{Andrius}{#1}}}

@@

\begin{table*}[t]
{\small
\begin{center}
\begin{tabular}{| l | >{\centering\arraybackslash}m{0.8cm} | >{\centering\arraybackslash}m{0.8cm} | >{\centering\arraybackslash}m{0.9cm} | >{\centering\arraybackslash}m{1.6cm} | >{\centering\arraybackslash}m{1.6cm} | >{\centering\arraybackslash}m{1.6cm} | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{1.cm} | }
\hline
    \textbf{Net ID} & \textbf{Country} & \textbf{No filter} & \textbf{Global IP}   & \textbf{Port-specific} & \textbf{Validate checksum} & \textbf{Drop S/A data} & \textbf{Normalize ACK}  & \textbf{Normalize URG} & \textbf{Normalize Reserved} & \textbf{Remap Seq.} \\ \hline \hline
    % Univ Helsinki WiFi
    WiFi edu 1      & FI               &                    &                      &                        & \checkmark \checkmark      &                        &                         &                        &                             &                     \\ \hline
    % Eduroam
    WiFi edu 2      & UK               &                    & \checkmark           &                        &                            & \checkmark             &                         & \checkmark \checkmark  &                             & \checkmark          \\ \hline
    % wgb
    WiFi pub 1      & UK               & \checkmark         &                      &                        &                            &                        &                         &                        &                             &                     \\ \hline
    % Virgin home
    WiFi res 1      & UK               &                    &                      &                        & \checkmark \checkmark      &                        &                         &                        &                             &                     \\ \hline
    \hline
    % Finland internet.saunalahti
    Cellular 1      & FI               & \checkmark      &                      &                        &                            &                        &                         &                        &                             &                     \\ \hline
    % GiffGaff
    Cellular 2      & UK               &                 &                      &  \checkmark (443, 993) & -                          & -                      & -                       & -                      & -                           & -                   \\ \hline            
\end{tabular}
\end{center}
}
\caption{Network behaviour observed through tests generating custom TCP packets. A single checkmark means that particular behaviour was observed or in case of normalization the field was reset or replaced with a valid value. Double checkmark means that specific type of packet was discarded. A dash means that we observed different cases on the same network.}
\label{tab:networks}
\end{table*}

We show our collected results in Table~\ref{tab:networks}. Since we were focusing on mobile applications, we collected data across a number of public, residential and university WiFi networks and cellular networks in XX different countries: UK, USA, Finland (pending: Turkey, India, Lithuania, Spain...). We picked the most important dimensions that show what modifications to the protocol have the highest chance of being successull across the largest number of networks. In particular, the results include which networks provided clients a global IP address (very few), which ones we did not see any filtering for (a relatively large, but insufficient number to take any deployment for granted), and which ones discarded packets with invalid checksums, normalised particular fields - either dropped packets or reset to different values - and what type of mapping did NATs perform - only port number remapping or also changed sequence numbers.

@@

\begin{quotation}
    Although these examples do not show connection synchronization using data-carrying segments, this is perfectly legitimate
\end{quotation}

We also tested middlebox itneraction with reserved header bits. We separated our tests to handshake and data exchange parts as well as set each bit individually, however we did not observe different behavior for these: all reserved bits were either allowed through or cleared at both phases. Importantly, we did not observe cases when such packets are dropped.
